Cut systems and matrix factorisations I

### 2016-11-02 cutsystems-new.tex
Real second arXiv submission, with updated title.
Updates

\title{Computing with cut systems}
\author{Daniel Murfet}

@@

The canonical action of $C_m$ on the spinor representation $S_m$ by wedge product and contraction $\{ \theta_i, \theta_i^* \}_{i=1}^m$ (see Lemma \ref{defn:spinorrep}) induces an action  of $C_m$ on $S_m \otimes_k ( Y \otimes X )$. In Section \ref{section:superbicatLG} we defined an action of $C_m$ on the cut $Y \l X$ by operators $\{ \ferm_i, \fermc_i \}_{i=1}^m$, and it remains to show that these two actions are compatible.

>>>>

\title{Cut systems and matrix factorisations I}
\author{Daniel Murfet}

% \classification{18D05, 18E30, 13C14}
%18D05  	Double categories, $2$-categories, bicategories and generalizations
%57R56  	Topological quantum field theories
%13C14		Cohen-Macaulay modules
%18E30		Derived and triangulated categories

@@

The canonical action of $C_m$ on the spinor representation $S_m$ by wedge product and contraction $\{ \theta_i, \theta_i^* \}_{i=1}^m$ (see Lemma \ref{defn:spinorrep}) induces an action  of $C_m$ on $S_m \otimes_k ( Y \otimes X )$. In Definition \ref{defn:cliffordaction_cut} we gave an action of $C_m$ on the cut $Y \l X$ by operators $\{ \ferm_i, \fermc_i \}_{i=1}^m$, and it remains to show that these two actions are compatible.
